Field-informed Reinforcement Learning for Learnining Large Scale Collective Tasks

### 2023-04-19 paper.tex

\usepackage[T1]{fontenc}
\usepackage{xcolor}
\def\doi#1{\href{https://doi.org/\detokenize{#1}}{\url{https://doi.org/\detokenize{#1}}}}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
%
\usepackage{listings}
\lstset{language=Pascal}
\begin{document}
%
\title{Field-informed Reinforcement Learning for Learnining Large Scale Collective Tasks} %% Todo improve
% or: Field-Informed Reinforcement Learning: A Scalable and Effective Method for Collective Intelligence
% or: A Novel Approach to Reinforcement Learning for Adaptive Collective Systems
%

@@

The remainder of this paper is structured as follows. First we introduce the relevant background and problem formulation. Afterwards we introduce our approach in Section~\ref{sec:approach}. Section~\ref{sec:eval} outlines the performed experiments and discusses the obtained results. Finally, we will present our conclusions in Section~\ref{sec:conclusion}.

\section{Background}
\label{sec:background}
\ga{Page budget: 1 page}

\section{Background and Motivation}
\ga{Page budget: 1 page}
\ga{Plan: discussed the problem of coordination in multi-agent systems 
and the need for a scalable approach. In doing this, we will discuss some of the existing approaches}
\subsection{Field Coordination Approaches}
\subsection{Many-Agent Reinforcement Learning}
\subsection{Graph Neural Network}

\section{Field-informed Reinforcement Learning}

\section{Approach}
\label{sec:approach}

\section{Evaluation}
\label{sec:eval}
\subsection{Simulation setup}
\subsection{Scenario}

@@

\section{Conclusion and Future Work}
\label{sec:conclusion}

>>>>

\usepackage[T1]{fontenc}
\usepackage{xcolor}
\usepackage{cleveref}
\def\doi#1{\href{https://doi.org/\detokenize{#1}}{\url{https://doi.org/\detokenize{#1}}}}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
%
\usepackage{listings}
\lstset{language=Pascal}
\begin{document}
%
\title{Field-informed Reinforcement Learning for Learnining Large Scale Collective Tasks} %% Todo improve
% or: Field-Informed Reinforcement Learning: A Scalable and Effective Method for Collective Intelligence
% or: A Novel Approach to Reinforcement Learning for Adaptive Collective Systems
%

@@

The remainder of this paper is structured as follows. First we introduce the relevant background and problem formulation in \Cref{sec:background}. Afterwards we introduce our approach in Section~\ref{sec:approach}. Section~\ref{sec:eval} outlines the performed experiments and discusses the obtained results. Finally, we will present our conclusions in Section~\ref{sec:conclusion}.

\section{Background and Motivation}
\label{sec:background}
\ga{Page budget: 1/2 page \\}
\ga{Plan: discussion about the problem of coordination in multi-agent systems 
and the need for a scalable approach. In doing this, we will discuss some of the existing approaches (declarative, RL and )}
\subsection{Field Coordination Approaches}
\ga{discussion about field used as a coordination mechanism in multi-agent systems. Introduction to AC}
\subsection{Graph Neural Networks for Multi-Agent Systems}
\subsection{Many-Agent Reinforcement Learning}
\ga{plan: we could discuss briefly about standard appraoch (few agents), mean field approach (many agents). This will led to our approach, which is a combination of DQN (or any Deep RL approach) and GNN.}

\section{Field-informed Reinforcement Learning}
\label{sec:approach}
\ga{Page budget: 2/3 pages \\}
\ga{Plan: we should discuss the approach in detail, including the system model, the learning dynamics.
Particularly, I would like to highlight how the each node in the graph is a local controller,
but it could be see as a global evolution, therefore we can use global information to inform the local controller.}
\subsection{System model}
\ga{Plan: 
  discussion about typical AC evalaution model, specifying how GNN (with 1-hop information diffusion)
  can be easily integrate with this distributed model
}
\subsection{Learning dynamics}
\ga{
  Plan: discuss about the choosing approach, that is Centralised Training and Distributed Execution.
  Particularly, we use DQN in which the neural network is a GNN. So, the dataset consist in a set of graphs,
  where each graph is a snapshot of the system. 
  The target is the Q-value of the action taken in the current state.
  Explain how this can be then use for distributed controller.
}
\section{Evaluation}
\label{sec:eval}
\ga{Page budget: 2 pages \\}
\ga{Plan: we should discuss the robot aggregation scenario, specifiying the state space, the action space, the reward function.
I dunno if it makes sense to discuss the variants (i.e., fixed area, two ares and moving area). We will see.
}
\subsection{Scenario}

@@

\subsection{Discussion and Results}
\section{Conclusion and Future Work}
\ga{Page budget: 0.5}
\label{sec:conclusion}
